Concurrent Programming with Harmony

### 2020-07-30 book/paper.tex
Latest

SBSs allow much control over which thread runs next and is therefore a
good starting point for developing fair synchronization algorithm
In this chapter, we will present two SBS-based fair reader/writer lock
implementations.
The first, in \autoref{fig:RWfair}, is based on \autoref{fig:RWsplitsema}.
There are two differences:

@@

In the late 70s, Xerox PARC developed a new programming language called
Mesa~\cite{LR80}.
\index{Mesa}%
Mesa introduced various important concepts to programming languages,
including software exceptions and incremental compilation.  Mesa also
incorporated a version of monitors.
However, there are some subtle but important differences with Hoare
monitors that make Mesa monitors quite unlike split binary semaphores.

As in Hoare monitors, there is a hidden mutex associated with each monitor,
and the mutex is automatically acquired upon entry to a method and released
upon exit.
Mesa monitors also have condition variable that a process can wait on.
Like in Hoare monitors, the \texttt{wait} operation releases the mutex.
The most important difference is in what \texttt{signal} does.
To make the distinction more clear, we shall call the corresponding Mesa
operation \texttt{notify} rather than \texttt{signal}.
\index{notify}%
When a process $p$ invokes \texttt{notify}, it does not immediately pass 
the baton to some process $q$ requiring the baton (assuming there even
is such a process).  Instead, $p$ holds onto
the baton until it leaves the monitor.  At that point, any process that
was notified will have a chance to obtain the baton.

>>>>

SBSs allow much control over which thread runs next and is therefore a
good starting point for developing fair synchronization algorithms.
In this chapter, we will present two SBS-based fair reader/writer lock
implementations.
The first, in \autoref{fig:RWfair}, is based on \autoref{fig:RWsplitsema}.
There are two differences:

@@

In the late 70s, researchers at Xerox PARC,
where among others the desktop and Ethernet
were invented, developed a new programming language called
Mesa~\cite{LR80}.
\index{Mesa}%
Mesa introduced various important concepts to programming languages,
including software exceptions and incremental compilation.  Mesa also
incorporated a version of monitors.
However, there are some subtle but important differences with Hoare
monitors that make Mesa monitors quite unlike split binary semaphores.

As in Hoare monitors, there is a hidden mutex associated with each monitor,
and the mutex is automatically acquired upon entry to a method and released
upon exit.
Mesa monitors also have condition variables that a process can wait on.
Like in Hoare monitors, the \texttt{wait} operation releases the mutex.
The most important difference is in what \texttt{signal} does.
To make the distinction more clear, we shall call the corresponding Mesa
operation \texttt{notify} rather than \texttt{signal}.
\index{notify}%
When a process $p$ invokes \texttt{notify}, it does not immediately pass 
the baton to some process $q$ requiring the baton (assuming there even
is such a process).  Instead, $p$ holds onto
the baton until it leaves the monitor.  At that point, any process that
was notified will have a chance to obtain the baton.
